---
title: "Week 2 Assignment"
author: "Hsin-Yi Chien"
date: "2022-09-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE, message=FALSE, warning=FALSE}
coves_fy22<-read.csv("FY22 COVES_labels.csv", header = TRUE)
attach(coves_fy22)
library(ggplot2)
library(dplyr)
library(stringr)
library(tidyverse)
library(tidytext)
library(rstatix)
```

# FY22 COVES Annual Report

Visitor Research and Evaluation (VRE) collected exit surveys between *July 1, 2021 and June 30, 2022* to gain a better understanding of our **visitor demographics** and **visitor experience** during their visit to the Exploratorium.

## Group Demographics

The COVES protocol involves selecting one adult from a visitor group to be the primary respondent, but the survey asks for some information that describes *the entire visiting group*.

### Group Size

-   **Average** number of *adults* in a group = 2.1
-   **Median** number of *adults* in a group = 2
-   **Average** number of *children* in a group = 0.95
-   **Median** number of *children* in a group = 1

```{r group-size, echo=TRUE, include=TRUE, message=FALSE, warning=FALSE}
#show the summary descriptives for the number of adults in sampled groups
round(summary(as.numeric(Nadults)),2)
round(sd(as.numeric(Nadults), na.rm = TRUE),2)
#show the summary descriptives for the number of children in sampled groups
round(summary(as.numeric(Nchild)),2)
round(sd(as.numeric(Nchild), na.rm = TRUE),2)
```

```{r pressure, echo=TRUE, include=TRUE, message=FALSE, warning=FALSE}
coves_fy22[!is.na(as.numeric(Nadults)), ] %>%
  ggplot(aes(x = as.numeric(Nadults))) +
  geom_histogram() +
  scale_x_continuous(breaks = seq(0:10))+
  labs(title = "Histogram of Number of Adults in a Group")+
  xlab("Number of Adults in a Group") +
  ylab("Count")
  
coves_fy22[!is.na(as.numeric(Nchild)), ] %>%
  ggplot(aes(x = as.numeric(Nchild))) +
  geom_histogram() +
  scale_x_continuous(breaks = seq(0:10))+
  labs(title = "Histogram of Number of Children in a Group")+
  xlab("Number of Children  in a Group") +
  ylab("Count")  

```
