---
title: "Week 4 Assignment"
author: "Hsin-Yi Chien"
date: "2022-10-11"
output: html_document
---

```{r setup, include= FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(janitor)
library(tidytext)
library(rstatix)
library(hrbrthemes)
library(ggthemes)

coves_fy22<-read_csv("FY22 COVES_values.csv") #import "FY22 COVES_values.csv" data

```

# FY22 COVES Annual Report

Visitor Research and Evaluation (VRE) collected exit surveys between *July 1, 2021 and June 30, 2022* to gain a better understanding of our **visitor demographics** and **visitor experience** during their visit to the Exploratorium.

## Group Size & Overall Experience Rating

```{r group-size, echo=TRUE, include=TRUE, message=FALSE, warning=FALSE}

#create a "group type" var based on whether there is any children in the group
for (i in (1:nrow(coves_fy22))){
  if (is.na(coves_fy22$Nchild[i])){
    coves_fy22$group_type[i] <- NA
  } else if (!is.na(coves_fy22$Nchild[i]) & coves_fy22$Nchild[i] == 0){
    coves_fy22$group_type[i] <-"Adult Only"
  } else if (!is.na(coves_fy22$Nchild[i]) & coves_fy22$Nchild[i] > 0){
    coves_fy22$group_type[i] <-"Family Group with Child(ren)"
  }
}

#check if the above scripts are successful
coves_fy22 %>%
  select(Nchild, group_type)

#add labels to OER
coves_fy22$OER<-factor(coves_fy22$OER, 
                       levels = c(1,2,3,4,5),
                       labels = c("Poor", "Fair", "Good", "Excellent", "Outstanding"), 
                       ordered = TRUE)

#show the frequency of OER by group type
OER_grouptype_tb<-coves_fy22 %>%
  drop_na(OER, group_type) %>%
  tabyl(OER, group_type) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1, rounding = "half up") %>%
  adorn_ns()

OER_grouptype_tb

#can you advise on a more efficient way to convert the crosstab outcome into a dataframe?
coves_fy22_OER_grouptype <- data.frame(
  OER = rep(levels(coves_fy22$OER),2),
  Group_Type = c(rep("Adult Only", 5), rep("Group with Children", 5)),
  n = c(c(0,5,62,349,376), c(0,1,52,370,456)),
  percentage = c(c(0, 0.6, 7.8, 44.1, 47.5), c(0, 0.1, 5.9, 42.1, 51.9)))

```

The following plot shows the breakdown of Overall Experience Rating by Group Type (Adult-only vs. Family Group):

```{r OER_group_type_plot, echo=TRUE, include=TRUE, message=FALSE, warning=FALSE}
coves_fy22_OER_grouptype %>%
  mutate(OER = fct_relevel(OER, "Poor", "Fair", "Good", "Excellent", "Outstanding")) %>%
  ggplot(aes(x = Group_Type, y = percentage, fill = OER))+
  geom_col(position = position_dodge()) +
  scale_fill_brewer(palette = "Blues") +
  theme_economist()+
  geom_text(aes(label= paste0(percentage, "%")), vjust=0, color="black",
            position = position_dodge(0.9), size= 3)+
  labs(title = "Overall Experience Rating by Group Type",
       x ="",
       y = "Percentage")+
  theme(legend.title=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y=element_blank())
```

